Manuscript draft

### 2019-09-11 manuscript/Discussion_KAT.Rmd
Update Discussion_KAT.Rmd

>>>>

There is strong evidence from our analyses that the latituidinal gradient in FACF (Figs. 2-3) is driven primarily by temperature-related climate variables (Figs. 4-5). Because many climate variables co-vary across the latitudinal gradient, because climatic drivers affect forest carbon flux on much shorter time scales than can be captured by annual climate summary variables, and because both climatic conditions and C flux vary interannually around long-term means, we would not expect a single  variable characterizing mean annual climate to adequately predict variation in FACF. However, it remains informative to consider these relationships.
